

\subsection{Standard Libraries} \label{stdlib}

\begin{tabular}{l L}
\TT{Logic} 	&
	Classical logic and dependent equality
\\	
\TT{Arith}		&
	Basic Peano arithmetic
\\
\TT{PArith} 	&
	Basic positive integer arithmetic
\\
\TT{NArith}  	&
	Basic binary natural number arithmetic
\\
\TT{ZArith} 	&
	Basic relative integer arithmetic
\\
\TT{Numbers} 	&
	Various approaches to natural, integer and cyclic numbers (currently axiomatically and on top of $2^{31}$ binary words)
\\
\TT{Bool} 		&
	Booleans (basic functions and results)
\\
\TT{Lists} 		& 
	Monomorphic and polymorphic lists (basic functions and results), Streams (infinite sequences defined with co-inductive types)
\\
\TT{Sets}		& 
	Sets (classical, constructive, finite, infinite, power set, etc.)
\\
\TT{FSets} 		&
	Specification and implementations of finite sets and finite maps (by lists and by AVL trees)
\\
\TT{Reals}		&
	Axiomatization of real numbers (classical, basic functions, integer part, fractional part, limit, derivative, Cauchy series, power series and results,...)
\\
\TT{Relations}		&
	Relations (definitions and basic results)
\\
\TT{Sorting}		&
	Sorted list (basic definitions and heapsort correctness)
\\
\TT{Strings} 		&
	8-bits characters and strings
\\
\TT{Wellfounded}		&
	Well-founded relations (basic results)
\\
\end{tabular}




\subsection{Require} \label{require}
To use the standard libraries or other compiled files, you first need to tell the environment that it needs to load the compiled file. 
\TT{Require} adds the specified module and all of its dependencies to the environment. 

\begin{code}
	\cmd{Require} Logic.
\end{code}

\noindent
\TT{Require Import} loads the specified module and its dependences, then imports the contents of the specified module.

\begin{code}
	\cmd{Require Import} Bool.
\end{code}

\noindent
\TT{Require Export} acts like \TT{Require Import}, but will ensure that any module B that uses \TT{Require Import} on the module A that contained the \TT{Require Export} command will import both module A and the one specified in the \TT{Require Export} command.

\begin{code}
	\cmd{Require Export} Bool.
\end{code}




\subsection{Load} \label{load}
This is used to load a file or library into the current environment. 
To load one of the standard libraries, you can simply use the \TT{Load} command.

\begin{code}
	\cmd{Load} Arith.
\end{code}

\noindent
However, to load any other existing file, you will likely need to specify where to look for the file; to do this, there is the 
\TT{Add LoadPath} command.
All the commands in the loaded file will be evaluated

\begin{code}
	\cmd{Add} LoadPath \str{``/myDirectory/path/"}. \\
	\cmd{Load} myFile. 
\end{code}








