
A simple example defining suits and values for cards, and what a valid card is. In the function \blue{check\_num}, we check if the number given is less than 11 and greater than 1. In function \blue{is\_valid\_card}, we pattern match against various types of cards. Here, the given card is represented by the variable x. The type card is defined to be \blue{c (s: suit) (v: val)}, and we know that an \blue{s} of type suit can only be one of the valid suits we defined, so we can use some variable, say \blue{q}, to represent allowing any suit type; the part we need to ensure is valid is the value given to the suit, since a valid card can only have a value of an ace, king, queen, jack, or number values 2 thru 10.

\begin{code}
\Load List. 	\\
\Load Bool.
\\ \\
\Inductive \nm{suit} : \Type :=
  $\mid$ heart
  $\mid$ diamond
  $\mid$ spade
  $\mid$ club.

\Inductive \nm{val} : \Type :=
  $\mid$ ace
  $\mid$ king
  $\mid$ queen
  $\mid$ jack
  $\mid$ num (n: nat).

\Inductive \nm{card} : \Type :=
  $\mid$ c (s: suit) (v: val).
\\ \\
\cmt{Card: 2 of Spades} 	\\
\Check (c spade (num 2)).
\\ \\
\cmt{List of suits}	\\
\Check (ace::king::[ ]).
\\ \\
\cmt{List of Cards} 	\\
\Check [c heart ace; c diamond king; c spade queen].
\\ \\
\Definition \nm{check\_num} (x: nat) : bool :=	 \\ \-\ \quad
  \If (x $<?$ 11)						 \\ \-\ \quad
  \Then \If (1 $<?$ x)					 \\ \-\ \qquad
       \Then true						 \\ \-\ \qquad
       \Else false						 \\ \-\ \quad
  \Else false.
%\\ \\
%Compute check\_num 0.
%Compute check\_num 1.
%Compute check\_num 2.
%Compute check\_num 10.
%Compute check\_num 11.
\\ \\
\Definition \nm{is\_valid\_card} (x: card) : bool :=	 \\ \-\ \quad
 \match x \with						 \\ \-\ \quad
  $\mid$ c q ace $=>$ true				 \\ \-\ \quad
  $\mid$ c q king $=>$ true			 \\ \-\ \quad
  $\mid$ c q queen $=>$ true			 \\ \-\ \quad
  $\mid$ c q jack $=>$ true			 \\ \-\ \quad
  $\mid$ c q (num n) $=>$ 				 \\ \-\ \qquad\quad
        \If (check\_num n)				 \\ \-\ \qquad\quad
        \Then true			 			 \\ \-\ \qquad\quad
        \Else false						 \\ \-\ \quad
 \End.
\\ \\
\cmt{Ace of Hearts is a valid card}	\\
Compute is\_valid\_card (c heart ace).
\\ \\
\cmt{11 of Diamonds is NOT a valid card}	\\
Compute is\_valid\_card (c diamond (num 11)).

%Compute is\_valid\_card (c heart (num 10)).
%Compute is\_valid\_card (c heart king).
%Compute is\_valid\_card (c heart queen).
%Compute is\_valid\_card (c heart jack).
%Compute is\_valid\_card (c heart (num 9)).
%Compute is\_valid\_card (c heart (num 1)).
%\Check (c heart ace).

\end{code}












